Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-18 pkg/disttree/inst/draft/rejoinder2.Rnw
final revision and formatting
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2470 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: bc69d6b1df1a94a14c4954e27896487bb7cffb6f

please find attached the revised version of our manuscript 
``Distributional regression forests for probabilistic precipitation 
forecasting in complex terrain'' (AOAS1804-015).

@@

East Tyrol differs from North Tyrol as it is located south of the main Alpine Ridge and thus
in a different climate zone. Consequently, both long-term climatological characteristics
and precipitation patterns in 2009--2012 differ. This is not visible from Figure~8 directly,
though, and hence we added a short explanation at the end of Section~3.4

@@

FIXME: Torsten, should we comment on this? In a predictive setup like the precipitation
forecasting the uncertainty of the estimates is not of so much concern. Also, the 
uncertainty due to variation in the response is typically much larger.

>>>>

please find attached the revised version of our manuscript 
``Distributional regression forests for probabilistic precipitation 
forecasting in complex terrain'' (AOAS1811-010).

@@

East Tyrol differs from North Tyrol as it is located south of the main Alpine Ridge and thus
in a different climate zone. Consequently, both long-term climatological characteristics
and precipitation patterns in 2009--2012 differ. This is not visible from Figure~8 directly,
though, and hence we added a short explanation at the end of Section~3.4.

@@
